On Devon Allen's Disqualification at the 2022 World Track and Field Championships

### 2023-10-16 Manuscript/manuscript.tex
Respond to Prof Schifano's comments

Table~\ref{tab:Clusrankresults} shows the results generated from both the 
permutation and asymptotic rank-based tests for the three comparisons, 
as discussed previously in Section~\ref{sec:rank}. The national versus international
comparison produced lower p-values than the 2019 versus 2022 comparison, with the
national vs international permutation test producing a p-value of $2\cdot10^{-6}$.
This is a highly significant test result and shows that athletes who competed at the
2022 World Track and Field Championships were on average, significantly faster
at reacting than they were just a few months prior. For the 2019 versus 2022
same athlete comparison with permutation test, the p-value was 
$0.003$, which is significant at $\alpha = 0.01$. 
\eds{According to the table, this p-value is 0.028 (significant at the 0.05 
level.)}
The result of
comparing 2022 and 2023 was very similar (but not exactly the same) to the above
result, as the p-value from the permutation test was $0.003$.
\eds{According to the table, this p-value is $0.011$.} 
Taken together, these three
tests help show that athletes competing at the 2022 World Track and Field
Championships had faster reaction times than when they had competed at other
competitions.

@@

Figure~\ref{fig:VenueEffects} further illustrates the venue effect from 1999 to
2023 based on the full GLMM both with and without 2022.  The temporal patterns
of the two sets of effects look very similar, except that the positive effects
estimated with 2022 included have higher magnitude than those estimated without
2022, which compensates the negative effect of the 2022 with a large magnitude.
Both plots agree to some extent with the pattern of the centers of the boxplots in
Figure~\ref{fig:Boxplot}. The mismatch is due to the venue effect, which has a
higher standard deviation than the venue effect. 
\eds{I do not understand what is meant by the previous sentence.}
The venue effect for 2022 is
lower than that for any other year, but may not be as extreme as one would
think considering the history of reaction times going back to 1999.

>>>>

Table~\ref{tab:Clusrankresults} shows the results generated from both the 
permutation and asymptotic rank-based tests for the three comparisons, 
as discussed previously in Section~\ref{sec:rank}. The national versus international
comparison produced lower p-values than the 2019 versus 2022 comparison, with the
national vs international permutation test producing a p-value of $2\cdot10^{-6}$.
This is a highly significant test result and shows that athletes who competed at the
2022 World Track and Field Championships were on average, significantly faster
at reacting than they were just a few months prior. For the 2019 versus 2022
same athlete comparison with permutation test, the p-value was 
$0.028$, which is significant at $\alpha = 0.05$. 
\eds{According to the table, this p-value is 0.028 (significant at the 0.05 
level.)}
\of{Resolved}
The result of
comparing 2022 and 2023 was very similar (but not exactly the same) to the above
result, as the p-value from the permutation test was $0.011$.
\eds{According to the table, this p-value is $0.011$.} 
\of{Resolved}
Taken together, these three
tests help show that athletes competing at the 2022 World Track and Field
Championships had faster reaction times than when they had competed at other
competitions.

@@

Figure~\ref{fig:VenueEffects} further illustrates the venue effect from 1999 to
2023 based on the full GLMM both with and without 2022.  The temporal patterns
of the two sets of effects look very similar, except that the positive effects
estimated with 2022 included have higher magnitude than those estimated without
2022, which compensates the negative effect of the 2022 with a large magnitude.
Both plots agree to some extent with the pattern of the boxplots in
Figure~\ref{fig:Boxplot}. The mismatch is due to the venue effect, which has a
higher standard deviation than the venue effect. 
\eds{I do not understand what is meant by the previous sentence.}
\of{I believe Prof Yan wrote that. I would write that sentence as "The mismatch
is due to the heat effect, as venue effect only captures a part of the patterns
in the data" or something of that nature.}

The venue effect for 2022 is
lower than that for any other year, but may not be as extreme as one would
think considering the history of reaction times going back to 1999.
